\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
Modified FreeFuzz code according to comments

\begin{lstlisting}[language=bash]
  ...
  ====== test session starts ======
  platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
  ...
  IndexError: list index out of range
  ====== 1 passed in 1.09s ======
  ...
  Updating environment in the container of the testing tool
  Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
  __pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
  ...
  Running the testing tool on the environment of the bug
  Testing on  ['torch']
  torch.log2
  ...
  torch.nn.MaxUnpool2d
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ...
\end{lstlisting}

\Fix{Consider the comments from Saikat, please.}
Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug. Then it proceeds to run the entire testing tool on the enviroment. After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool. In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.

>>>>

\begin{lstlisting}[language=bash]
  ...
  [Reproducing the bug]
  ====== test session starts ======
  platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
  ...
  IndexError: list index out of range
  ====== 1 passed in 1.09s ======
  ...
  [Setting up FreeFuzz]
  Updating environment in the container of the testing tool
  Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
  __pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
  ...
  [Running FreeFuzz]
  Running the testing tool on the environment of the bug
  Testing on  ['torch']
  torch.log2
  ...
  torch.nn.MaxUnpool2d
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ...
\end{lstlisting}

% \Fix{Consider the comments from Saikat, please.}
Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug. Then it proceeds to run the entire testing tool on the enviroment. After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool. In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.
